A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS

### 2020-02-24 analysis/paper.Rmd
add debug code in the regression and add some explanation

# Result

>>>>

We revised some parts of the regression model and found inconsistent variable names during the debugging process for the reproduction of the tables and figures to be sucessful. In the following section of the original regression code, we changed the parameter in the bootstrapping model from 1:500 to 1:5 to make it run faster. We also caught the inconsistency in the variable  “lambda.min” where the parameter should be “lambda” from the model.

```{r, eval=FALSE}
 boot_models <- list(length=5)
    t0 <- predict(best.fitting.model,newx = x,s="lambda.min") %>% as.vector
    tt <- boot_models[1:5] %>%purrr::map(~predict(best.fitting.model,newx = x,s="lambda.min") %>% as.vector) %>% unlist()
    #lambda <- best.fitting.model$lambda.min
    lambda <- best.fitting.model$lambda
    theta <- as.matrix(coef(best.fitting.model, s = "lambda.min"))
    pi_hat <- predict(best.fitting.model, newx = x, s = "lambda.min", type = "response")
    n <- length(pi_hat)
    y_star <- sapply(seq_len(length(tt)), function(i) ifelse(runif(n) <= pi_hat, 1, 0))
    suff_stat <- t(y_star) %*% x
```
# Result
